---
title: "R Programming Final Project"
author: "Brandon Ly"
date: "4/27/2022"
output: html_document
---
[Github](https://github.com/BrandonSchoolPF/Package)

****

## What is a Prime Number?

A prime number is an integer in which two whole numbers cannot be multiplied to 
get that integer.  

For example, 4 is not a prime number because 2x2 = 4. But, 5 is a prime number
because no two same whole numbers can be multiplied in order to get 5.  

****

## 'ly' Package

The Package that I have created contains the function 'is.prime()' where if you
input an integer it will return a logical answer of either TRUE or FALSE.

```{r}
library(ly)

is.prime(4)

is.prime(5)
```

As we can see here, the first command is.prime(4) returned a false statement 
because as stated before, 4 is not a prime number because two equal whole numbers
can be multiplied together in order to get 4, but 5 does not.  

If we were to use a data frame we could use this function to test if an 
observation is a prime number or not.

```{r}
head(mtcars)

is.prime(mtcars[1,3])
```
The Mazda RX4 displacement or engine size of 160 is not a prime number. 

***

## How it Works

Taking a look at the script that provides the function, the function only 
contains an if else statement. 

```{r}
is.prime <- function(x) {
  if (x == 2) {
    TRUE
  } else if (any(x %% 2:(x-1) == 0)) {
    FALSE
  } else {
    TRUE
  }
}
```

If we were to get a number that is greater than 2 (1 is considered not a prime
 number), if that number can divide itself by 2 with both products equaling to 
 each other but not also equal to 0 then the function will return TRUE, if not 
 it will return FALSE.
 
```{r}
is.prime <- function(x) {
  if (x == 2) {
    TRUE
  } else if (any(x %% 2:(x-1) == 0)) {
    FALSE
  } else {
    TRUE
  }
}

is.prime(574389)
```

